Characterizing Stellar Streams by ML

### 2023-08-26 src/tex/ms.tex
[showyourwork] overleaf sync

        \todo[inline]{TODO: how much should be included here?}

@@

    In this section we present an application of our model to a synthetic stream with known ground truths, and demonstrate the model's ability to characterize stream density variations and membership probabilities in an unsupervised manner.
    % We then apply the method to real stellar streams in \autoref{sec:results_gd1} and \autoref{sec:results_pal5}.

@@

        \begin{figure*}
            \script{mock/plot/results.py}
            \centering
            \includegraphics[width=1\linewidth]{figures/mock/results.pdf}
            \caption{
                %
                \textbf{Top panel:}%
                The stream mixture coefficient $f(\phi_1)$ 
                Stream fraction.
                %
                \textbf{Middle panel:}%
                $\phi_2(\phi_1)$
                %
                \textbf{Lower panel 3:}%
                %
                \textbf{Upper Histograms:}%
                %
                \textbf{Upper Middle Histograms:}%
                %
                \textbf{Lower Middle Histograms:}%
                %
                \textbf{Lower Histograms:}%
            }
            TODO:
            \begin{enumerate}
                \item the linear density in the stream-fraction plot
            \end{enumerate}
            \label{fig:mock_data_result}
        \end{figure*}

@@

    % sub: test_on_a_synthetic_stream (end)

>>>>

@@

    In this section we present an application of our model to a synthetic stream with known ground truths, and demonstrate the model's ability to characterize stream density variations and membership probabilities in an unsupervised manner.

@@

    \begin{figure*}
        \script{mock/plot/results.py}
        \centering
        \includegraphics[width=1\linewidth]{figures/mock/results.pdf}
        \caption{
            %
            \textbf{Top panel:}%
                The stream mixture coefficient $f(\phi_1)$ (black dotted line) predicted by the model, overplotted on the true stream fraction (black-outlined histogram),
                calculated as the ratio of stream stars to total stars in 55 bins
                over the $\phi_1$ range of the isochrone.
            \textbf{Middle panel: }%
                $\phi_2(\phi_1)$ over the full range of $\phi_1$. The data color and transparency is set by the model's MLE stream probability (with dropout turned off). Plotted behind the data are the true labels for the stream stars (large black circles).
                The true labels exactly limn the model-identified stream stars.
                The MLE stream track (black dashed line) is over-plotted on the probability-colored data.
            %
            \textbf{Lower panel 3: }%
                $\varpi_2(\phi_1)$ over the full range of $\phi_1$. Like for $\phi_2$, the data color and transparency is set by the MLE probability, with the true labels (large black circles) under-plotted and MLE track (black dashed line) over-plotted.
            %
            \textbf{Upper Histograms: }%
                $\phi_2$ histograms for each model component (blue background, red stream), in 4 $\phi_1$ ranges across the data set.
                The height of each bin is the probability-weighted density.
                The background is a uniform distribution, while the stream is a Gaussian. In projection across the $\phi_1$ range it can appear multi-modal (panel 2) if there are large gaps or `smeared' out if the Gaussian's mean changes significantly over the range.
            %
            \textbf{Upper Middle Histograms: }%
                Parallax $\varpi$ histograms for each model component (blue background, red stream), in 4 $\phi_1$ ranges across the data set.
                The height of each bin is the probability-weighted density.
            %
            \textbf{Lower Middle and Lower Histograms:}%
                Photometric coordinate $(g, r)$ plots for each model component in 4 $\phi_1$ ranges across the data set. The top row plots the stream stars (red) over the background. The lower row plots the background stars (blue) over the stream stars to show that the
                how the two distributions mix.
        }
        TODO:
        \begin{enumerate}
            \item the linear density in the stream-fraction plot
        \end{enumerate}
        \label{fig:mock_data_result}
    \end{figure*}

@@

% sec: test_on_a_synthetic_stream (end)
